True versus apparent shapes of astrophysical bow shocks

### 2015-06-29 papers/Paper1/sec-intro.tex
New start on Jorge's paper
Paper1: Add bibliography and make start on intro
All references should go in bowshocks-biblio.bib

\section{Generic bow shock model}
\label{sec:generic-model}

>>>>

\section{Introduction}
\label{sec:intro}

%%
%% Circumstances when bowshocks arise
%%

The archetypical bow shock is formed when a solid body moves
supersonically through a compressible fluid.  Terrestrial examples
include the atmospheric re-entry of a space capsule, or the sonic boom
produced by a supersonic jet \citep{van-Dyke:1982a}.  In astrophysics
the term bow shock is employed more widely, to refer to many different
types of curved shocks that have approximate cylindrical symmetry.

%%
%% Examples of astrophysical bowshocks
%%

%% 
%% Restriction to cylindrical symmetry
%%

For simplicity, the current paper is restricted to cylindrically
symmetric bowshock shapes.
